Handling String-Number Conversion in String Constraint Solving

### 2019-11-19 evaluation.tex
add a missing hline in table 2
fix some typos

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3211 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    15 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    17 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r}
\hline
\multicolumn{2}{c}{}                   & Z3-Trau & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{StrInt}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline
\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
							& unsat    &  1054*  & 780* & 1043* &  634* \\
							& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
\multirow{3}{*}{leetcode-add\_Binary}	& sat & 520*  &  530* &  531* &  11* \\ 
							& unsat    &  1351*  & 1091* & 1091* &  1094* \\
							& $\times$ &  11*  &  261* &  260* & 777* \\ \hline
\multirow{3}{*}{leetcode-numDecodings}	& sat & 166*  &  107* &  151* &  50* \\ 
							& unsat    &  273*  & 269* & 283* &  269* \\
							& $\times$ &  92*  &  155* &  97* & 212* \\ \hline
\multirow{3}{*}{leetcode-restoreIpAddresses}	& sat & 811*  &  462* &  864* &  55* \\ 
							& unsat    &  13648*  & 13540* & 13648* &  13342* \\
							& $\times$ &  54*  &  511* &  1* & 1116* \\ \hline
\multirow{3}{*}{leetcode-validIPAddress}	& sat & 54*  &  57* &  58* &  8* \\ 
							& unsat    &  19*  & 19* & 19* &  19* \\
							& $\times$ &  4*  &  1* &  0* & 50* \\ \hline
\multirow{3}{*}{leetcode-validWordAbbreviation}	& sat & 183*  &  193* &  188* &  8* \\ 
							& unsat    &  24*  & 11* & 21* &  16* \\
							& $\times$ &  39*  &  42* &  37* & 222* \\ \hline
\multirow{3}{*}{lib-datetime\_parse\_hh\_mm\_ss\_ff}	& sat &  133*  & 133* &  133* &  88* \\ 
							& unsat    &  41*  & 41* & 41* &  43* \\
							& $\times$ &  0*  &  0* &  0* & 43* \\ \hline
\multirow{3}{*}{lib-datetime\_parse\_isoformat\_date}	& sat & 32*  &  32* &  32* &  23* \\ 
							& unsat    &  0*  & 0* & 0* &  0* \\
							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
\multirow{3}{*}{lib-distutils\_get\_build\_version}	& sat & 19*  &  19* &  19* &  4* \\ 
							& unsat    &  24*  & 24* & 24* &  24* \\
							& $\times$ &  0*  &  0* &  0* & 15* \\ \hline
\multirow{3}{*}{lib-email\_parsedate\_tz}	& sat & 68*  &  72* &  72* &  30* \\ 
							& unsat    &  138*  & 138* & 138* &  138* \\
							& $\times$ &  4*  &  0* &  0* & 42* \\ \hline
\multirow{3}{*}{lib-http\_parse\_request}	& sat & 24*  &  24* &  24* &  8* \\ 
							& unsat    &  9*  & 9* & 9* &  7* \\
							& $\times$ &  0*  &  0* &  0* & 18* \\ \hline
\multirow{3}{*}{lib-ipaddress\_ip\_int\_from\_string}	& sat & 595*  &  204* &  480* &  18* \\ 
							& unsat    &  427*  & 373* & 431* &  357* \\
							& $\times$ &  1006*  &  1451* &  1117* & 1653* \\ \hline
\multirow{3}{*}{lib-nntplib\_parse\_datetime}	& sat & 4*  &  8* &  0* &  0* \\ 
							& unsat    &  0*  & 0* & 0* &  0* \\
							& $\times$ &  4*  &  0* &  8* & 8* \\ \hline
\multirow{3}{*}{lib-smtpd\_parseargs}	& sat & 27*  &  27* &  27* &  24* \\ 
							& unsat    &  72*  & 72* & 72* &  66* \\
							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
\multirow{3}{*}{lib-wsgiref\_check\_status}	& sat & 10*  &  10* &  10* &  6* \\ 
							& unsat    &  9*  & 9* & 9* &  9* \\
							& $\times$ &  0*  &  0* &  0* & 4* \\ \hline
% \multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* \\
% 									& unsat    &   2912*  &  2211* &  2655* &   1944* \\
% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}

\hide{  % 2nd version of tables
\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & Z3-Trau & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                           & Z3-Trau & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

\hide{  % 1st version of tables
\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}
}

@@

We compare {\tool }with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We present data on two benchmark groups that demonstrate two points. First, {\tool} is the most efficient tool for formulas that contain string-number conversion constraints. Second, {\tool} is among the best tools in on benchmarks without string-number conversion constraints.
The results of the experiments is summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas. Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crashed).

>>>>

\begin{table*}[t]
\centering
\caption{Results of z3-Trau, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{3}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& $\times$ &  1977*   &  1824* &  3211 &  18558*  & 2444 & 25421 & 24439 \\ \hline
\multirow{3}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& $\times$ &   185*   &   174* &   481 &    451*  & 386 & 309 & 599 \\ \hline
\multirow{3}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& $\times$ &    26*   &    21* &     0 &    216*  & 61 & 2666 & 890 \\ \hline
\multirow{3}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& $\times$ &   269*   &   148* &   549 &    382*  & 38 & 468 & 1065 \\\hline
\multirow{3}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& $\times$ &     5*   &     6* &    15 &     55*  & 88 & 76 & 797 \\ \hline
\multirow{3}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& $\times$ &     2*   &   101* &    17 &     71*  & 137 & 120 & 978 \\ \hline
\multirow{3}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& $\times$ & 0* & 0* & 3391 & 1186* & 84 & 383 & 13 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\scalebox{0.7}{
\begin{tabular}{l r | r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4   &    Z3  & Z3-str3 \\ \hline
\multirow{3}{*}{StrInt}		& sat      &   3294*  &  2185* &  2731* &    422* \\ 
							& unsat    &  17088*  & 16377* & 16832* &  16034* \\
							& $\times$ &   1191*  &  3011* &  2010* &   5117* \\ \hline \hline
\multirow{3}{*}{leetcode-addStrings}	& sat & 622*  &  330* &  100* &  85* \\ 
							& unsat    &  1054*  & 780* & 1043* &  634* \\
							& $\times$ &  2*  &  568* &  535* & 959* \\ \hline
\multirow{3}{*}{leetcode-add\_Binary}	& sat & 520*  &  530* &  531* &  11* \\ 
							& unsat    &  1351*  & 1091* & 1091* &  1094* \\
							& $\times$ &  11*  &  261* &  260* & 777* \\ \hline
\multirow{3}{*}{leetcode-numDecodings}	& sat & 166*  &  107* &  151* &  50* \\ 
							& unsat    &  273*  & 269* & 283* &  269* \\
							& $\times$ &  92*  &  155* &  97* & 212* \\ \hline
\multirow{3}{*}{leetcode-restoreIpAddresses}	& sat & 811*  &  462* &  864* &  55* \\ 
							& unsat    &  13648*  & 13540* & 13648* &  13342* \\
							& $\times$ &  54*  &  511* &  1* & 1116* \\ \hline
\multirow{3}{*}{leetcode-validIPAddress}	& sat & 54*  &  57* &  58* &  8* \\ 
							& unsat    &  19*  & 19* & 19* &  19* \\
							& $\times$ &  4*  &  1* &  0* & 50* \\ \hline
\multirow{3}{*}{leetcode-validWordAbbreviation}	& sat & 183*  &  193* &  188* &  8* \\ 
							& unsat    &  24*  & 11* & 21* &  16* \\
							& $\times$ &  39*  &  42* &  37* & 222* \\ \hline
\multirow{3}{*}{lib-datetime\_parse\_hh\_mm\_ss\_ff}	& sat &  133*  & 133* &  133* &  88* \\ 
							& unsat    &  41*  & 41* & 41* &  43* \\
							& $\times$ &  0*  &  0* &  0* & 43* \\ \hline
\multirow{3}{*}{lib-datetime\_parse\_isoformat\_date}	& sat & 32*  &  32* &  32* &  23* \\ 
							& unsat    &  0*  & 0* & 0* &  0* \\
							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
\multirow{3}{*}{lib-distutils\_get\_build\_version}	& sat & 19*  &  19* &  19* &  4* \\ 
							& unsat    &  24*  & 24* & 24* &  24* \\
							& $\times$ &  0*  &  0* &  0* & 15* \\ \hline
\multirow{3}{*}{lib-email\_parsedate\_tz}	& sat & 68*  &  72* &  72* &  30* \\ 
							& unsat    &  138*  & 138* & 138* &  138* \\
							& $\times$ &  4*  &  0* &  0* & 42* \\ \hline
\multirow{3}{*}{lib-http\_parse\_request}	& sat & 24*  &  24* &  24* &  8* \\ 
							& unsat    &  9*  & 9* & 9* &  7* \\
							& $\times$ &  0*  &  0* &  0* & 18* \\ \hline
\multirow{3}{*}{lib-ipaddress\_ip\_int\_from\_string}	& sat & 595*  &  204* &  480* &  18* \\ 
							& unsat    &  427*  & 373* & 431* &  357* \\
							& $\times$ &  1006*  &  1451* &  1117* & 1653* \\ \hline
\multirow{3}{*}{lib-nntplib\_parse\_datetime}	& sat & 4*  &  8* &  0* &  0* \\ 
							& unsat    &  0*  & 0* & 0* &  0* \\
							& $\times$ &  4*  &  0* &  8* & 8* \\ \hline
\multirow{3}{*}{lib-smtpd\_parseargs}	& sat & 27*  &  27* &  27* &  24* \\ 
							& unsat    &  72*  & 72* & 72* &  66* \\
							& $\times$ &  0*  &  0* &  0* & 9* \\ \hline
\multirow{3}{*}{lib-wsgiref\_check\_status}	& sat & 10*  &  10* &  10* &  6* \\ 
							& unsat    &  9*  & 9* & 9* &  9* \\
							& $\times$ &  0*  &  0* &  0* & 4* \\ \hline
% \multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* \\
% 									& unsat    &   2912*  &  2211* &  2655* &   1944* \\
% 									& $\times$ &   1203*  &  2975* &  2012* &   5028* \\ \hline
\end{tabular}}
\label{table:str_int_benchmark}
\end{table}

\hide{  % 2nd version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                   & {\tool} & CVC4  &    Z3 & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{PyEx}		& sat      & 19586*   & 19763* & 18359 &   3024*  & 19149 & 0 & 111 \\ 
							& unsat    &  3858*   &  3834* &  3851 &   3839*  & 3828 & 0 & 871 \\
							& timeout  &  1969*   &     0* &  3211 &  16708*  & 2444 & 0 & 44 \\
							& $\times$ &     8*   &  1824* &     0 &   1850*  & 0 & 25421 & 24395 \\ \hline
\multirow{4}{*}{APLAS}		& sat      &   128*   &   205* &    19 &     38*  & 132 & 289 & 0 \\
							& unsat    &   287*   &   211* &   100 &    111*  & 82 & 2 & 1 \\
							& timeout  &   185*   &   174* &   481 &     93*  & 386 & 308 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    358*  & 0 & 1 & 599 \\ \hline
\multirow{4}{*}{LeetCode}	& sat      &   856*   &   860* &   881 &    670*  & 778 & 0 & 158 \\
							& unsat    &  1784*   &  1785* &  1785 &   1780*  & 1827 & 0 & 1618 \\
							& timeout  &    26*   &    21* &     0 &     83*  & 15 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &    133*  & 46 & 2666 & 890 \\ \hline
\multirow{4}{*}{StringFuzz}	& sat      &   502*   &   677* &   311 &    493*  & 688 & 439 & 0 \\
							& unsat    &   294*   &   240* &   205 &    190*  & 339 & 158 & 0 \\
							& timeout  &   267*   &    63* &   549 &    377*  & 29 & 297 & 0 \\
							& $\times$ &     2*   &    85* &     0 &      5*  & 9 & 171 & 1065 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{pred}} & sat & 16* & 11* &   12 &      8*  & 247 & 316 & 21 \\
							& unsat    &   814*   &   818* &   808 &    772*  & 500 & 443 & 17 \\
							& timeout  &     5*   &     6* &    15 &     41*  & 23 & 0 & 0 \\
							& $\times$ &     0*   &     0* &     0 &     14*  & 65 & 76 & 797 \\ \hline
\multirow{4}{*}{cvc4\textsubscript{term}} & sat & 13* & 8* &     6 &     16*  & 311 & 576 & 45 \\
							& unsat    &  1030*   &   936* &  1022 &    958*  & 596 & 349 & 22 \\
							& timeout  &     2*   &    12* &    17 &     53*  & 50 & 0 & 0 \\
							& $\times$ &     0*   &    89* &     0 &     18*  & 87 & 120 & 978 \\ \hline
\multirow{4}{*}{SLOG}  		& sat      & 0* & 1309* & 0 & 0* & 1228 & 1036 & 1299 \\
							& unsat    & 3391* & 2082* & 0 & 2205* & 2079 & 1972 & 2079 \\
							& timeout  & 0* & 0* & 631 & 1186* & 84 & 361 & 9 \\
							& $\times$ & 0* & 0* & 2760 & 0* & 0 & 22 & 4 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}

\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on str\_int benchmark (numbers with * will be updated later)}
\begin{tabular}{l r | r r r r r r r}
\hline
\multicolumn{2}{c}{}                           & {\tool} & CVC4   &    Z3  & Z3-str3 & Trau+ & ABC & Ostrich \\ \hline
\multirow{4}{*}{full\_str\_int}		& sat      &   3294*  &  2185* &   422* &   2731* & 158 & 0 & 47 \\ 
									& unsat    &  17088*  & 16377* & 16034* &  16832* & 1609 & 0 & 213 \\
									& timeout  &   1191*  &  3011* &  4131* &   2010* & 439 & 0 & 144 \\
									& $\times$ &      0*  &     0* &   986* &      0* & 19367 & 21573 & 21169 \\ \hline
\multirow{4}{*}{filtered\_str\_int}	& sat      &   3281*  &  2210* &  2729* &    424* & 159 & 0 & 47 \\
									& unsat    &   2912*  &  2211* &  2655* &   1944* & 70 & 0 & 0 \\
									& timeout  &   1203*  &  2975* &  2012* &   4106* & 475 & 0 & 119 \\
									& $\times$ &     0*   &     0* &     0* &    922* & 6492 & 7396 & 7230 \\ \hline
\end{tabular}
\label{table:str_int_benchmark}
\end{table*}
}

\hide{  % 1st version of tables
\begin{table*}[t]
\centering
\caption{Results of {\tool}, cvc4, and z3 on string benchmarks}
\begin{tabular}{l | r r r | r r r | r r r | r r r}
\hline
\multirow{2}{*}{}   & \multicolumn{3}{|c|}{z3-Trau} & \multicolumn{3}{|c}{cvc4} & \multicolumn{3}{|c}{z3} & \multicolumn{3}{|c}{z3-str3} \\
			& sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ & sat & unsat & timeout/$\times$ \\ \hline
PyEx		& 19586 & 3858 & 1969/8 & 19763 & 3834 & 0/1824 & 16581 & 3832 & 5008/0 & 3024 & 3839 & 16708/1850 \\ 
APLAS		&   128 &  287 &  185/0 & 205 &  221 & 174/0 &  13 &  100 & 486/1 & 38 & 111 & 93/358 \\ 
LeetCode	&   856 & 1784 &   26/0 & 860 & 1785 &  21/0 & 881 & 1785 & 0/0 & 670 & 1780 &  83/133 \\ 
StringFuzz	& 502 & 294 & 267/2 & 677 & 240 & 63/85 & 265 & 187 & 609/4 & 493 & 190 & 377/5 \\ 
cvc4\textsubscript{pred}	& 16 & 814 & 5/0 & 11 & 818 & 6/0 & 12 & 808 & 15/0 & 8 & 772 & 41/14 \\ 
cvc4\textsubscript{term}	& 13 & 1030 & 2/0 & 8 & 936 & 12/89 & 5 & 1021 & 19/0 & 16 & 958 & 53/18 \\ \hline
\end{tabular}
\label{table:base_benchmark}
\end{table*}
}

@@

We compare {\tool} with other state-of-the-art string solvers, namely CVC4~\cite{cvc4Tool}, Z3~\cite{z3}, \textsf{z3str3}~\cite{zheng2013z3}, Ostrich~\cite{chen2019decision} and \textsf{Trau+}~\cite{parosh2019chain}. We do not compare with Sloth \cite{sloth} since it does not support length constraints, which occurs in most of our benchmarks. We present data on two benchmark groups that demonstrate two points. First, {\tool} is the most efficient tool for formulas that contain string-number conversion constraints. Second, {\tool} is among the best tools in on benchmarks without string-number conversion constraints.
The results of the experiments is summarized in Table~\ref{table:base_benchmark} and Table~\ref{table:str_int_benchmark}, respectively. All experiments were executed on a computer with 4-core CPU, 8 GiB RAM and Ubuntu 18.4-LVM OS. The timeout was set to 10s for each test. Columns with heading \texttt{sat}/\texttt{unsat} show numbers of solved formulas. Columns with heading $\times$ indicate the number of instances the solver fails (including timeout, report unknown, report incorrect result, or crashed).
